U07m with Indices
========================================================

Just make sure to create the project directory in ProjectTemplate first, then create the project in RStudio using the existing directory.

To create a new project called my-project, open R and type:
library('ProjectTemplate')
create.project('my-project')

To enter that project’s home directory and start working, type:
setwd('my-project')
setwd("~/Dropbox/R/CompetitionIndexer")

load.project()
I have a already made a project called CompetitionIndexer.Rproj in the directory of Home/Dropbox/R/CompetitionIndexer


Once you have code worth testing, you can also type,
run.tests()
to automatically run all of the unit tests in your tests directory.
To do work on such a project, enter the main directory, open R and type source('lib/boot.R'). This will then automatically perform the following actions:

    source('lib/load_libraries.R'), which automatically loads the CRAN packages currently deemed best practices. At present, this list includes:
        reshape
        plyr
        stringr
        ggplot2
        testthat
    source('lib/load_data.R'), which automatically imports any CSV or TSV data files inside of the data/ directory.
    source('lib/preprocess_data.R'), which allows you to make any run-time modifications to your data sets automatically. This is blank by default.


```{r ProjectTemplate}
#create.project('CompetitionIndexer')
setwd("~/Dropbox/R/CompetitionIndexer")
library('ProjectTemplate')
#using load.project() will run a global.dcf config script that will load a bunch of helper functions, packages, and data sets
load.project()
#source('/usr/lib/R/library/load_libraries.R')
#??Searchpath
.libPaths()
```
Loading libraries, not necessary if load.project() works
```{r load libraries}
library("ggplot2", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("Hmisc", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("knitr", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("markdown", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("MASS", lib.loc="/usr/lib/R/library")
library("mgcv", lib.loc="/usr/lib/R/library")
library("MVA", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("plyr", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
# library("Rcmdr", lib.loc="/usr/lib/R/site-library")
library("rstudio", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
library("shiny", lib.loc="/home/bradfordbender/R/x86_64-pc-linux-gnu-library/3.0")
```
Load U07m cleaned 9 year data (0 dbh's made "na")
```{r load data make boxplots}

U07mData<- read.csv("~/Dropbox/R/CompetitionIndexer/data/U07m2013Cleaned.csv")

df<-U07mData
# Check out first rows of data, and structure of the fields
head(df)
str(df)
# make a boxplot of the dbh's grouped by progeny name
boxplot(dbh~name,na.rm=TRUE,data=df)  # not ordered by median
# compute index of ordered 'name' and reassign          
oind <- order(as.numeric(by(df$dbh, df$name, median,na.rm=TRUE)))
oind
df$name<- ordered(df$name, levels=levels(df$name)[oind])

boxplot(dbh ~ name, data=df, na.rm=TRUE,xlab="Full Sib Progeny Name",ylab="9-yr DBH (inches)",main="U07m-2005 alba/aspen Full Sib Progeny Trial (NM6 check clone)") # now it is ordered by median
#####
###help for this ordering from website 
###< http://stackoverflow.com/questions/3765950/sorting-a-boxplot-based-on-median-value >

```
```{r ggplot2 boxplots}
# control the amount of jitter
p<-qplot(factor(name),dbh, data = df,  geom="boxplot",na.rm=TRUE,xlab="Full Sib Progeny Name",ylab="9-yr DBH (inches)",main="U07m-2005 alba/aspen Full Sib Progeny Trial (NM6 check clone)")
p + geom_boxplot() + 
  geom_jitter(aes(color=name),position=position_jitter(width=.1 ))+ 
  theme(axis.text.x = element_text(angle=-90,vjust=0.5, hjust=1))

```
Other ggplot2 options for graphing
```{r ggplot2 options}
p + geom_boxplot(aes(fill = factor(name))+theme(axis.text.x = element_text(angle=-90,vjust=0.5, hjust=1)))

p + geom_boxplot(notch=TRUE)+ geom_jitter(aes(color=name))+ 
  theme(axis.text.x = element_text(angle=-90,vjust=0.5, hjust=1))

p + geom_boxplot(notch=FALSE)+ geom_jitter(aes(color=name)+ 
    theme(axis.text.x = element_text(angle=-90,vjust=0.5, hjust=1)))
p + geom_boxplot(geom='error bar',notch=FALSE)+ geom_jitter(aes(color=name))


```
website help: < http://www.statmethods.net/advgraphs/ggplot2.html > 
qplot(x, y, data=, color=, shape=, size=, alpha=, geom=, method=, formula=, facets=, xlim=, ylim= xlab=, ylab=, main=, sub=) 
option   description
alpha 	Alpha transparency for overlapping elements expressed as a fraction between 0 (complete transparency) and 1 (complete opacity)
color, shape, size, fill 	Associates the levels of variable with symbol color, shape, or size. For line plots, color associates levels of a variable with line color. For density and box plots, fill associates fill colors with a variable. Legends are drawn automatically.
data 	Specifies a data frame
facets 	Creates a trellis graph by specifying conditioning variables. Its value is expressed as rowvar ~ colvar. To create trellis graphs based on a single conditioning variable, use rowvar~. or .~colvar)
geom 	Specifies the geometric objects that define the graph type. The geom option is expressed as a character vector with one or more entries. geom values include "point", "smooth", "boxplot", "line", "histogram", "density", "bar", and "jitter".
main, sub 	Character vectors specifying the title and subtitle
method, formula 	If geom="smooth", a loess fit line and confidence limits are added by default. When the number of observations is greater than 1,000, a more efficient smoothing algorithm is employed. Methods include "lm" for regression, "gam" for generalized additive models, and "rlm" for robust regression. The formula parameter gives the form of the fit.

For example, to add simple linear regression lines, you'd specify geom="smooth", method="lm", formula=y~x. Changing the formula to y~poly(x,2) would produce a quadratic fit. Note that the formula uses the letters x and y, not the names of the variables.

For method="gam", be sure to load the mgcv package. For method="rml", load the MASS package.
x, y 	Specifies the variables placed on the horizontal and vertical axis. For univariate plots (for example, histograms), omit y
xlab, ylab 	Character vectors specifying horizontal and vertical axis labels
xlim,ylim 	Two-element numeric vectors giving the minimum and maximum values for the horizontal and vertical axes, respectively


# Separate regressions of mpg on weight for each number of cylinders

qplot(wt, mpg, data=mtcars, geom=c("point", "smooth"),
   method="lm", formula=y~x, color=cyl,
   main="Regression of MPG on Weight",
   xlab="Weight", ylab="Miles per Gallon")



