U07m with Indices
========================================================

Just make sure to create the project directory in ProjectTemplate first, then create the project in RStudio using the existing directory.

To create a new project called my-project, open R and type:
library('ProjectTemplate')
create.project('my-project')

To enter that project’s home directory and start working, type:
setwd('my-project')
load.project()

Once you have code worth testing, you can also type,
run.tests()
to automatically run all of the unit tests in your tests directory.
To do work on such a project, enter the main directory, open R and type source('lib/boot.R'). This will then automatically perform the following actions:

    source('lib/load_libraries.R'), which automatically loads the CRAN packages currently deemed best practices. At present, this list includes:
        reshape
        plyr
        stringr
        ggplot2
        testthat
    source('lib/load_data.R'), which automatically imports any CSV or TSV data files inside of the data/ directory.
    source('lib/preprocess_data.R'), which allows you to make any run-time modifications to your data sets automatically. This is blank by default.


```{r ProjectTemplate}
library('ProjectTemplate')
create.project('CompetitionIndexer')
setwd('CompetitionIndexer')
load.project()
#source('/usr/lib/R/library/load_libraries.R')
#??Searchpath
.libPaths()
U07mData<-read.csv("~/R/CompetitionIndexer/data/U07m2013Cleaned.csv",header=TRUE)
head(U07mData)
str(U07mData)
boxplot(dbh~name,na.rm=TRUE,data=U07mData)  # not ordered by median
# compute index of ordered 'cost factor' and reassign          
oind <- order(as.numeric(by(U07mData$dbh, U07mData$name, median,na.rm=TRUE)))
oind
U07mMedian<-by(U07mData$dbh, U07mData$name, median,na.rm=TRUE)
U07mMedian
U07mData$name<- ordered(U07mData$name, levels=levels(U07mData$name)[oind])

boxplot(dbh ~ name, data=U07mData, na.rm=TRUE,xlab="Full Sib Progeny Name",ylab="9-yr DBH (inches)",main="U07m-2005 alba/aspen Full Sib Progeny Trial (NM6 check clone)") # now it is ordered by median
#####
###help for this ordering from website 
###< http://stackoverflow.com/questions/3765950/sorting-a-boxplot-based-on-median-value >

```

You can also embed plots, for example:

```{r Deducer Generated Code}
JGR()
### reading in data to Deducer
U07m2013Cleaned <- read.table("/home/bradfordbender/R/CompetitionIndexer/data/U07m2013Cleaned.csv",header=T,sep=",",quote="")



```

