U08as Competition Data Analysis
========================================================
seting environment at MSU desktop computer
```{r set environment MSU} 
setwd("C:/Users/Brad/Dropbox/R/CompetitionIndexer")
library("Deducer", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("DeducerANOVA", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("DeducerExtras", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("knitr", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("manipulate", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("markdown", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("mgcv", lib.loc="C:/Program Files/R/R-3.0.2/library")
library("shiny", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("UsingR", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")
library("plotrix", lib.loc="C:/Users/Brad/Documents/R/win-library/3.0")


```
Set environment on Linux laptop
```{r set environment laptop}
setwd("~/Dropbox/R/CompetitionIndexer")
library('ProjectTemplate')
#using load.project() will run a global.dcf config script that will load a bunch of helper functions, packages, and data sets
load.project()
```
Loading the Project Template and running startup scripts
```{r ProjectTemplate}
library('ProjectTemplate')
load.project()
```

Loading data input to MSU windows desktop on dropbox directory
```{r input data MSU}
## some people do not realize that the 'colClasses' argument in
#      read.table() is quite useful -- can avoid explicit conversion
#d <- read.csv("C:/Users/Brad/Dropbox/R/CompetitionIndexer/data/u08asbasm1.csv",
 # header = TRUE, colClasses = c("factor","factor","numeric","numeric"))
# reading in Competition Indexer output file for U08as
d<-U08asCI.Output <- read.csv("C:/Users/Brad/Dropbox/R/CompetitionIndexer/data/U08asCI-Output.csv")
str(d)
length(d$dbh)
#subsetting rows, removing dbh NA values
ds<-subset(d,d$dbh!="NA" & d$block!="5")
length(ds$dbh)
dss<-subset(ds,select=c(block,dbh,year,name,stemno,htave,basm,Area_Index,DBH_Ratio))
length(dss$dbh)
str(dss)
dss$block<-as.factor(dss$block)
str(dss)
```
Loading data on linux laptop on dropbox directory
```{r input data laptop}
## some people do not realize that the 'colClasses' argument in
#      read.table() is quite useful -- can avoid explicit conversion
d <- read.csv("~/Dropbox/R/CompetitionIndexer/data/u08asbasm1.csv",           
  header = TRUE, colClasses = c("factor","factor","numeric","numeric"))
str(d)
```
Making a plot with ggplot2
```{r ggplot2}
## ggplot2 version: geom = 'jitter'
library(ggplot2)
#qplot(clone, basm, data = d, colour = clone, geom = "jitter")

oind <- order(as.numeric(by(dss$basm, dss$name, median,na.rm=TRUE)))
oind
dss$name<- ordered(dss$name, levels=levels(dss$name)[oind])

#boxplot(basm ~ clone, data=d, na.rm=TRUE,xlab="Full Sib Progeny Name",ylab="4-yr basal area (square meters / hectare)",main="U08as-2010 alba clonal Trial (NM6 check clone)") # now it is ordered by median
# control the amount of jitter
p<-qplot(factor(name),basm, data = dss,  geom="boxplot",na.rm=TRUE,xlab="Clone Name",ylab="Basal Area (M^2 / ha)",main="U08as-2010 alba clonal Trial 4-year data (NM6 check clone)")
p + geom_boxplot() + geom_jitter(aes(color=name)) + theme(axis.text.x = element_text(angle=-90,vjust=0.5, hjust=1))
# make stripchart or point graph
# order by mean rather than median
oind <- order(as.numeric(by(dss$basm, dss$name, mean,na.rm=TRUE)))
oind
dss$name<- ordered(dss$name, levels=levels(dss$name)[oind])


sc<-qplot(factor(name),basm,data=dss, geom="point",xlab="Family Member",ylab="Basal Area (Square Meters/Stool)",main="Figure 4. Variation in basal area per stool among clonal copies of 15 full-sibs \n of Populus alba family 83xAA04 after 4 growing seasons in a clonal trial \n in Escanaba, Michigan, USA" )
#grid(nx=NULL,ny=NULL, lty=1, lwd = 2)
#sc+ geom_point()+  geom_jitter(aes(color=clone))
#sc+ geom_point(position=position_dodge(height=.9),aes(group=clone))
#+ position_dodge(width=.1,aes(group=clone))
#+ geom_jitter(position=position_jitter(width=.1))

stripchart(dss$basm~dss$name,vertical=TRUE,method="stack",pch=19,
           xlab="Family Member",
           ylab="Basal Area (Square Meters/Stool)",
           main="Figure 4. Variation in basal area per stool among clonal copies of 15 full-sibs \n of Populus alba family 83xAA04 after 4 growing seasons in a clonal trial \n in Escanaba, Michigan, USA")
points(tapply(dss$basm, dss$name, mean,na.rm=TRUE), pch = 3,col="red")
# Display both cross hairs and grid lines.
#axis(2, col="red",lty=2, lwd=0.5)
grid(nx=NULL,ny=NULL, lty="dashed", lwd = 1)
warnings()
length(dss$basm)
           
```
looking at dbh and Area_Index
```{r Competition Index}
aov1<-aov(basm~name,data=dss)
summary(aov1)
boxplot(basm~name,data=dss)
aov2<-aov(basm~name+block, data=dss)
